---
title: "EDA Diamonds 3"
author: "Francia Moscoso"
date: "March 20, 2016"
output: html_document
---
setwd("~/SprintboardProject")

**Loading Libraries and 'diamonds' data set**
```{r LoadLib, message=F, warning=F}
library(ggplot2)
library(gridExtra)
library(dplyr)
```


To silence the execution of the library function eg.library(dplyr), use statement: {r message=F, warning=F}
```{r loadDiamonds, comment="", echo=TRUE}
data("diamonds")
str(diamonds)
```
<br>
**Create a histogram of diamond prices. Facet the histogram by diamond color
and use cut to color the histogram bars. The plot should look something like this: http://i.imgur.com/b5xyrOu.jpg**
**Note: In the link, a color palette of type 'qual' was used to color the histogram using scale_fill_brewer(type = 'qual')**

```{r}
ggplot(diamonds, aes(x = price, fill=cut)) +
geom_histogram(binwidth = 1000) + facet_wrap(~color) + scale_fill_brewer(type="qual")
```


**Create a scatterplot of diamond price vs. table and color the points by the cut of the diamond. The plot should look something like this: http://i.imgur.com/rQF9jQr.jpg. Note: In the link, a color palette of type 'qual' was used to color the scatterplot using scale_color_brewer(type = 'qual')**
```{r}
ggplot(diamonds, aes(x=table, y =price, color=cut)) +
       geom_point(alpha=1/2,position="jitter") +
       xlim(50,80) +   
       scale_color_brewer(type="qual")
```
<br>
```{r}
ggplot(diamonds, aes(x=table, y =price, color=cut)) +
       geom_point(alpha=1/20,size = 5, position=position_jitter(h=0)) +
       xlim(50,80) +  
       scale_color_brewer(type="qual")
```
<br>
This graphic looks much better with alpha=1/2 and size = 2.5 and scale_x_countinuos (eliminate the xlim).
```{r}
ggplot(diamonds, aes(x=table, y =price, color=cut)) +
       geom_jitter(alpha=1/2,size = 2.5, position=position_jitter(h=0)) +
       scale_x_continuous(breaks = seq(50, 80, by=2), limits = c(50,80)) +
       scale_color_brewer(type="qual")
```
<br>
<br>
**What is the typical table range for the majority of diamonds of ideal cut?**
53 to 57
<br>
<br>
**What is the typical table range for the majority of diamonds of premium cut?**
58 to 61
<br>
<br>
**Create a scatterplot of diamond price vs.volume (x * y * z) and color the points by the clarity of diamonds. Use scale on the y-axis to take the log10 of price. You should also omit the top 1% of diamond volumes from the plot. Note: Volume is a very rough approximation of a diamond's actual volume. The plot should look something like this. http://i.imgur.com/excUpea.jpg. In the link, a color palette of type 'div' was used to color the scatterplot using scale_color_brewer(type = 'div')**

```{r}
diamonds$volumen <- (diamonds$x*diamonds$y*diamonds$z)
max(diamonds$volumen)
Vol99 <- quantile(diamonds$volumen, probs = 0.99, na.rm = FALSE,type = 7)

ggplot(diamonds, aes(x=(x*y*z), y=price, color=clarity)) +
         scale_y_log10() +
       geom_jitter(alpha=1/2,size = 3, position=position_jitter(h=0)) +
       scale_x_continuous(name="Volumen",breaks = seq(0, Vol99, by=100),
                         limits = c(0,Vol99)) +
       scale_color_brewer(type="div")

```


**Proportion of Friendships Initiated:**<br>
**Many interesting variables are derived from two or more others. For example, we might wonder how much of a person's network on a service like Facebook the user actively initiated. Two users with the same degree (or number of friends) might be very different if one initiated most of those connections on the
service, while the other initiated very few. So it could be useful to consider this proportion of existing friendships that the user initiated. This might be a good predictor of how active a user is compared with their peers, or other traits, such as personality (i.e., is this person an extrovert?). Your task is to create a new variable called 'prop_initiated' in the Pseudo-Facebook data set. The varpf
iable should contain the proportion of friendships that the user initiated.**


```{r  comment="", echo=TRUE}
setwd("~/SprintboardProject")
pf <- read.csv("pseudo_facebook.csv",header=TRUE)
head(pf)
```
<br>
```{r comment="", echo=TRUE}
pf$prop_initiated <- (pf$friendships_initiated/pf$friend_count)
summary(pf$prop_initiated)
```


<br> 

**prop_initiated vs. tenure:**<br>
**Create a line graph of the median proportion of friendships initiated ('prop_initiated') vs.tenure and color the line segment by year_joined.bucket.Recall, we created year_joined.bucket in Lesson 5 by first creating year_joined from the variable tenure. Then, we used the cut function on year_joined to create four bins or cohorts of users:**<br>
**(2004, 2009], (2009, 2011], (2011, 2012], (2012, 2014]**<br>
**The plot should look something like this http://i.imgur.com/vNjPtDh.jpg
OR this http://i.imgur.com/IBN1ufQ.jpg**

Create variable 'year_joined': 
```{r comment="", echo=TRUE}
pf$year_joined <- floor(2014 - pf$tenure/365)
summary(pf$year_joined)
```
<br>
table of variable 'year_joined'
```{r comment="", echo=TRUE}
table(pf$year_joined)
```
<br>
Cut variable year_joined to create 4 bins or buckets of users.
```{r comment="", echo=TRUE}
pf$year_joined.bucket <- cut(pf$year_joined, 
                        c(2004,2009,2011,2012,2014))
head(pf$year_joined.bucket)
```
<br>
ggplot tenure vs. prop_initiated. 
```{r}
ggplot(aes(x=tenure,y=prop_initiated),data = subset(pf, !is.na(year_joined.bucket))) +
  xlab("Tenure") +
  ylab("Proportion of Friendships Initiated") +
  geom_line(aes(color=year_joined.bucket),stat="summary",fun.y=median)
```
<br>
<br>
**Smooth the last plot you created of of prop_initiated vs tenure colored by
year_joined.bucket. You can bin together ranges of tenure or add a smoother to the plot. There won't be a solution image for this exercise. You will answer some questions about your plot in the next two exercises.**
Adding Smooth by multiplying and dividing age by 30.
```{r}
ggplot(aes(x=(30*round(tenure/30)),y=prop_initiated),data = subset(pf, !is.na(year_joined.bucket))) +
  xlab("Tenure") +
  ylab("Proportion of Friendships Initiated") +
  geom_line(aes(color=year_joined.bucket),stat="summary",fun.y=median)
```
<br>
Using 'geom_smooth' to Smooth graphic.
```{r}
ggplot(aes(x=tenure,y=prop_initiated),data = subset(pf, tenure>=1)) +
  geom_smooth(aes(color=year_joined.bucket))
```
<br>
<br>
**On average, which group initiated the greaters poportion of its Facebook frienship, the plot with the smoother that you created in the last exercise can help you answer this question**<br>
**People who joined prior to 2009<br>
People who joined prior to 2009-2011<br>
People who joined prior to 2011-2012<br>
People who joined after 2012**<br>
Answer: People who joined after 2012.
<br>
<br>
**For the group with the largest proportion of frienship initiated, what is the groups's average (mean) proportion of friends initiated?**<br>
```{r comment="", echo=TRUE}
joined_after_2012 <- pf%>% filter(year_joined > 2012, !is.na(prop_initiated)) 
mean(joined_after_2012$prop_initiated)
```
<br>
Another way to see the result is by getting the summary of proportion of friendship by the group of proportion of friends initiated:<br>
```{r comment="", echo=TRUE}
by(pf$prop_initiated,pf$year_joined.bucket, summary)
```
<br>
Calculating the 'mean' using chaning command.
```{r comment="", echo=TRUE}
pf%>% filter(year_joined > 2012, !is.na(prop_initiated)) %>% select(prop_initiated)  %>%  summarise(mean (prop_initiated)) 
```
<br>
<br>
**Why do you think this group's proportion of frienship initiated is higher than the others?**<br>
Perhaps because there was a high number of friends already members in FB when new members joined after 2012 and they initiated the frienship. 
<br>
<br>
**Create a scatter plot of the price/carat ratio of diamonds. The variable x should be assigned to cut. The points should be colored by diamond color, and the plot should be faceted by clarity. The plot should look something like this http://i.imgur.com/YzbWkHT.jpg.Note: In the link, a color palette of type
'div' was used to color the histogram using scale_color_brewer(type = 'div')**

```{r}
ggplot(diamonds, aes(x=cut, y =price/carat, color=color)) +
       facet_wrap(~clarity) +
       geom_jitter(alpha=1/2, position=position_jitter(h=0)) +
       scale_color_brewer(type="div")
```
<br>
<br>
<br>
